Estimating real-time highstreet footfall from Wi-Fi probe requests

### 2018-06-20 paper/sections/pilot_study.tex
wed end of the day

>>>>

we find that the methodology works as shown by the reduction in the
mean error
We find kmeans and quantile best algorithms for filtering
sequencing works. Even in densely populated areas.

Though this is promising we need to know more to generalise the methodology.
we do a detailed multi location, longer term study with multiple manual
verification which is the main study.
